\section*{Executive Summary}
\addcontentsline{toc}{section}{Executive Summary}

\textbf{Repository URL:} \url{https://github.com/Ben-W-Yal/Good_Vibes_Final_Project}

GeoIntel is an impactful, game-changing intelligence application that redefines how people interact with news and understand modern conflicts. Built with a TypeScript/React and Express stack plus Gemini-powered generative AI, the system fuses social and open-source signals into one operational view so users can move from information overload to actionable understanding. Instead of passively reading disconnected headlines, users engage an interactive geospatial platform that combines event streams, mobility tracking, and AI briefing outputs to interpret what is happening, why it matters, and what is likely to happen next.

The interface pairs narrative intelligence with geographic grounding: grounded web research surfaces relevant article imagery where available, so users see visual context alongside text; users control an interactive 3D globe with terrain and building visualization (via Cesium ion) to pan, tilt, and zoom through the physical environment where events unfold. Selecting a specific event also triggers an \textbf{AI analyst summary} and an optional \textbf{chat} interface for follow-up questions scoped to that event's data. That combination supports a clearer mental map of borders, urban fabric, coastal access, elevation, and regional layout---helping users relate headlines to real geography rather than abstract place names alone.

A core methodological contribution is the Kalman filter framing: the model \emph{predicts} from prior posts and historical signal behavior, then \emph{measures} against fresh web-search evidence and current trend and market indicators. This predict-measure-update loop supports continuous state estimation of conflict and risk dynamics, producing more stable and decision-ready insights than raw feed monitoring alone. The result is a practical decision-support tool for analysts, operators, policy audiences, and business stakeholders who need faster situational awareness with transparent AI-assisted synthesis.
