\phantomsection
\addcontentsline{toc}{section}{References}

\begin{thebibliography}{99}

\bibitem{gemini-api}
Google.
\newblock \emph{Gemini API documentation} (Google AI for Developers).
\newblock \url{https://ai.google.dev/gemini-api/docs}

\bibitem{cesium}
Cesium GS, Inc.
\newblock \emph{Cesium ion and CesiumJS platform documentation}.
\newblock \url{https://cesium.com/learn/}

\bibitem{celestrak}
CelesTrak.
\newblock \emph{Satellite orbital data and TLE resources}.
\newblock \url{https://celestrak.org/}

\bibitem{gdelt}
GDELT Project.
\newblock \emph{The GDELT Project: Global Database of Events, Language, and Tone}.
\newblock \url{https://www.gdeltproject.org/}

\bibitem{acled}
Raleigh, Clionadh, Andrew Linke, H\aa{}vard Hegre, and Joakim Karlsen.
\newblock ``Introducing ACLED: Armed Conflict Location and Event Data.''
\newblock \emph{Journal of Peace Research}, 2010.
\newblock Project site: \url{https://acleddata.com/}

\bibitem{opensky}
OpenSky Network.
\newblock \emph{OpenSky API / state vector documentation}.
\newblock \url{https://openskynetwork.github.io/opensky-api/}

\bibitem{express}
OpenJS Foundation and contributors.
\newblock \emph{Express: web framework for Node.js}.
\newblock \url{https://expressjs.com/}

\bibitem{react}
Meta Open Source and contributors.
\newblock \emph{React documentation}.
\newblock \url{https://react.dev/}

\bibitem{course-req}
Zaman, Tauhid.
\newblock ``Final Project --- Generative AI and Social Media'' (course requirements).
\newblock Yale School of Management / course site.
\newblock \url{https://zlisto.github.io/genAI_social_media/project_requirements.html}

\end{thebibliography}
